\documentclass{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage{graphicx,wrapfig,lipsum}
\usepackage[export]{adjustbox}
\graphicspath{{./}}
\usepackage{float}
\usepackage[margin=.35in]{geometry}

\renewcommand{\maketitle}{
\begin{center}
{\huge\bfseries\theauthor}
\end{center}
}

\titleformat{\section}
{\huge\bfseries}
{}
{0em}
{} [\titlerule]

\titleformat{\subsection}
{\bfseries}
{}
{0em}
{}
\titlespacing{\subsection}
{0em}{.25em}{0em}

\title{Curriculum Vitae}
\author{Arián Luca Mateos  \\
\large   Data Scientist | Computer Scientist} 


\begin{document}
\maketitle
\section{Contact}
\begin{description}

\item[Certificate] https://www.datacamp.com/certificate/DSA0010324382061
\item[E-mail:]arianmateos@gmail.com
\item[Linkedin:] www.linkedin.com/in/arián-luca-mateos-164a83214

\item[GitHub:] https://github.com/PeachGB

\item[Date of Birth:]03/04/2001 

\item[Cellphone:]2216319417

\item[Postal Code:]1925

\item[City:]Ensenada, Buenos Aires, Argentina
\item[Availability:] Full Time

\end{description}
\section{Professional Profile}
Motivated Computer Engineering and Data Science student with a strong foundation in computer science and practical experience in programming, operating systems, and network administration. Skilled in data manipulation, visualization, and machine learning using Pandas, Matplotlib, and Scikit-learn. Proficient in SQL and PostgreSQL. Passionate about continuous learning and applying my knowledge to solve real-world problems through innovative projects. Equipped with strong problem-solving abilities and a commitment to staying updated with the latest technological advancements.
\section{Experience}
\subsection{Portfolio}

Developed and maintained a repository named "Data Projects" on GitHub, showcasing various data science projects.
\subsection{Network Technician Assistant}
Configured routers and managed service orders, 
ensuring optimal network performance and customer satisfaction.
\subsection{Programming and Math Tutor}
Provided secondary level tutoring in programming and mathematics, helping students improve their understanding and academic performance.
\subsection{Family Pizzeria}
Managed customer service, staff coordination, stock counting, and cooking, ensuring smooth operations and high-quality service.
\subsection{Ligantex Paint Stores (Family Franchise)}
Worked as a cashier and provided customer service, contributing to daily business operations and customer satisfaction.

\section{Skills}
\subsection{Workflow}
NeoVim, Tmux, Sway/i3 Window Manager, Git, Github-Cli,
gdb, R
\subsection{Data Science}
Data Analysis, Statistics, Tableau, Pandas, Matplotlib, Scikit-learn, Tensorflow,
Machine Learning, R, PostgreSQL
\subsection{Systems Administration}
GNU/Linux, Microsoft Azure, Nginx, Windows,
Docker, Virtualization, Networking.
\subsection{Software Development}
Github, Low-level Programming,
Algorithms and Data Structures,
Web Design.
\subsection{Multimedia}
Gimp, Canva
\subsection{General}
Mathematics,
Problem Solving, PC Repair,
Working under pressure, Customer Service,

\section{Languages}
\subsection{Programming and Scripting}
Rust,Go,C,  C++, Java, Python, Bash, R, JavaScript.
\subsection{DataBases}
SQL.
\subsection{Markup}
{\LaTeX}, HTML, Markdown, R-Markdown.
\subsection{Spoken}
English(Advanced), Spanish(Native)
\section{Education}
\subsection{University}
Computer Engineering | UNLP(2023-2027)\
Data Science in Organizations | UNLP(2024 2027-)
\subsection{High School}
Bachelor in Social and Human Sciences | EESN8 Ensenada
\subsection{Certification}
Data Scientist Associate Certificate | Data Camp

\end{document}
